\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-03-17 chapters/1_intro.tex
Partial algorithm description; add new figs/tables
Add and update graphics

\section{Introduction}
On possible selling story could be: currently many of the successful proposal-free instance segmentation methods rely on a final clustering step on a grid-graph with both short and long-range connections. So it is worth to study this problem in more details.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.pdf} % left bottom right top
\caption{\small 
Intro image: explain algorithm, main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

\section{Introduction}
%On possible selling story could be: currently many of the successful proposal-free instance segmentation methods rely on a final clustering step on a grid-graph with both short and long-range connections. So it is worth to study this problem in more details.

### 2019-03-17 chapters/3_algorithm.tex
Add and update graphics

\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/edge_contraction.png}
\caption{\small 
Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph.  \TODO{Rotate drawings to optimize space} \TODO{Add some cannot-link constraints to explain their propagation}
\label{fig:edge_contraction_and_contr_graph} }
\end{figure}

@@

\begin{itemize}
\item Define graph formalism and clustering $\Pi$. Make comment about special case of unsigned graph
\item Define multicut and associated energy
\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster. (the alg. will introduce them dynamically...)
\item Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e. a function of all the edge weights connecting the two clusters:
\begin{equation} \label{eq:linkage_criterion_def}
\begin{gathered}
\mathcal{L}(S_1,S_2) = \mathcal{L}(\mathcal{W})\quad \\
   \text{where} \quad \mathcal{W} = \{ W(e_{uv})| u\in S_1, v\in S_2 \}.
\end{gathered}
\end{equation}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
\caption{\small 
Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph...  
\label{fig:edge_contraction_and_contr_graph} }
\end{figure}

@@

\begin{itemize}
\item Define graph formalism and clustering $\Pi$. Make comment about special case of unsigned graph
\item Define multicut and associated energy

\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster. (the alg. will introduce them dynamically...)
\item Define contracted graph and edge contraction (explain Fig. 2)
\item Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e. a function of all the edge weights connecting the two clusters:
\begin{equation} \label{eq:linkage_criterion_def}
\begin{gathered}
\mathcal{L}(S_1,S_2) = \mathcal{L}(\mathcal{W})\quad \\
   \text{where} \quad \mathcal{W} = \{ W(e_{uv})| u\in S_1, v\in S_2 \}.
\end{gathered}
\end{equation}

### 2019-03-17 chapters/5_experiments_cityscapes.tex
Complete description of the algorithm
Add and update graphics

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{c| c| c | c}
        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
\textbf{mean} & False & {\color{ForestGreen} 0.3429 } & {\color{ForestGreen} 0.5516 } \\
% MEAN finetuned affs avg thresh035 use log costs & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
mean & True & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
% MEAN constr finetuned affs avg thresh035 use log costs & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
sum & False & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
% GAEC finetuned affs avg thresh035 dont use log costs & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Results on cityscapes validation set (with finetuned affinities)}
    \label{tab:linkage-criteria}
\end{table*}

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{c| c| c | c}
        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
    \label{tab:linkage-criteria}
\end{table*}

% \begin{table*}
%     \centering
%     \begin{subtable}[t!]{0.98\textwidth}\centering
%         \begin{tabular}{c| c | c | c}
% Update rule & \makecell{Use Cannot-Link\\Constraints} & \makecell{Multicut objective} & Runtime (s)\\ \midrule\midrule
% sum & false & \textbf{-150873} & 99 (??) \\
% sum & true & -150873 & 249 \\
% MutexWatershed & false & -150854 & 100 \\
% mean & false & -150850 & 105 \\
% mean & true & -150848 & 244 \\
% max & true & -149441 & 459 \\
% min & true & -147663 & 186 \\
% min & false & -147663 & 82 \\
% max & false & -103614 & \textbf{16} \\
%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Compare update-rules on fruit-fly large graph}
%     \label{tab:linkage-criteria}
% \end{table*}

>>>>

\begin{table}
    \centering
    \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{c| c| c | c }
        \makecell{Update rule \\ and CLC} & \makecell{Bias \\factor $\beta$} & AP & AP 50\%\\ \midrule\midrule
mean F & 0.35  & {\color{ForestGreen} 0.3429 } & {\color{ForestGreen} 0.5516 } \\
% MEAN & 0.35 & True & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
% MEAN & 0.30 & False & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5457 } \\
\cite{liu2018affinity} & -  & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
% MEAN & 0.40 & - & {\color{ForestGreen} 0.3402 } & {\color{ForestGreen} 0.5502 } \\
mean T & 0.25  & {\color{Orange} 0.3390 } & {\color{ForestGreen} 0.5481 } \\
% MEANconstr & 0.30 & False & {\color{Orange} 0.3344 } & {\color{ForestGreen} 0.5469 } \\
% MEAN & 0.45 & - & {\color{Orange} 0.3333 } & {\color{ForestGreen} 0.5438 } \\
% MEAN & 0.50 & - & {\color{Orange} 0.3255 } & {\color{ForestGreen} 0.5341 } \\
max T & 0.50  & {\color{Orange} 0.3252 } & {\color{ForestGreen} 0.5304 } \\
MWS & 0.45  & {\color{Orange} 0.3214 } & {\color{ForestGreen} 0.5306 } \\
sum T & 0.55  & {\color{Orange} 0.3188 } & {\color{Orange} 0.5271 } \\
% greedyFixation & 0.50 & - & {\color{Orange} 0.3180 } & {\color{Orange} 0.5155 } \\
% MEANconstr & 0.20 & False & {\color{Orange} 0.3161 } & {\color{Orange} 0.5136 } \\
% MutexWatershed & 0.50 & - & {\color{Orange} 0.3158 } & {\color{Orange} 0.5246 } \\
% MEANconstr & 0.35 & False & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
% greedyFixation & 0.60 & - & {\color{Orange} 0.3135 } & {\color{Orange} 0.5196 } \\
sum T & 0.55  & {\color{Orange} 0.3127 } & {\color{Orange} 0.5114 } \\
% GAEC & 0.50 & - & {\color{Orange} 0.3112 } & {\color{Orange} 0.5085 } \\
% SingleLinkagePlusCLC & 0.45 & - & {\color{Orange} 0.3109 } & {\color{Orange} 0.5134 } \\
% GAEC & 0.60 & - & {\color{Orange} 0.3100 } & {\color{Orange} 0.5120 } \\
% greedyFixation & 0.65 & - & {\color{Orange} 0.3056 } & {\color{Orange} 0.5063 } \\
% greedyFixation & 0.45 & - & {\color{Orange} 0.3045 } & {\color{Red} 0.4989 } \\
% GAEC & 0.65 & - & {\color{Orange} 0.3035 } & {\color{Orange} 0.5072 } \\
% GAEC & 0.45 & - & {\color{Orange} 0.3008 } & {\color{Red} 0.4956 } \\
% MEANconstr & 0.35 & True & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
% MEANconstr & 0.40 & False & {\color{Red} 0.2983 } & {\color{Orange} 0.5076 } \\
% GAEC & 0.70 & - & {\color{Red} 0.2943 } & {\color{Red} 0.4989 } \\
% SingleLinkagePlusCLC & 0.55 & - & {\color{Red} 0.2942 } & {\color{Orange} 0.5074 } \\
% greedyFixation & 0.70 & - & {\color{Red} 0.2919 } & {\color{Red} 0.4906 } \\
% GAEC & 0.75 & - & {\color{Red} 0.2793 } & {\color{Red} 0.4784 } \\
% greedyFixation & 0.75 & - & {\color{Red} 0.2750 } & {\color{Red} 0.4707 } \\
% SingleLinkagePlusCLC & 0.60 & - & {\color{Red} 0.2681 } & {\color{Red} 0.4744 } \\
% GAEC & 0.35 & True & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
% greedyFixation & 0.35 & - & {\color{Red} 0.2587 } & {\color{Red} 0.4484 } \\
% MutexWatershed & 0.40 & - & {\color{Red} 0.2562 } & {\color{Red} 0.4505 } \\
% MEANconstr & 0.50 & - & {\color{Red} 0.2507 } & {\color{Red} 0.4443 } \\
% SingleLinkagePlusCLC & 0.40 & - & {\color{Red} 0.2490 } & {\color{Red} 0.4411 } \\
% SingleLinkagePlusCLC & 0.65 & - & {\color{Red} 0.2489 } & {\color{Red} 0.4401 } \\
% greedyFixation & 0.35 & - & {\color{Red} 0.2438 } & {\color{Red} 0.4297 } \\
max F & 0.85 & {\color{Red} 0.2433 } & {\color{Red} 0.4436 } \\
% GAEC & 0.35 & False & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\
% SingleLinkage & 0.80 & - & {\color{Red} 0.2336 } & {\color{Red} 0.4265 } \\
% SingleLinkagePlusCLC & 0.70 & - & {\color{Red} 0.2285 } & {\color{Red} 0.4045 } \\
% SingleLinkage & 0.75 & - & {\color{Red} 0.2265 } & {\color{Red} 0.4065 } \\
% MutexWatershed & 0.35 & - & {\color{Red} 0.2253 } & {\color{Red} 0.4004 } \\
% SingleLinkage & 0.70 & - & {\color{Red} 0.2213 } & {\color{Red} 0.3947 } \\
% SingleLinkagePlusCLC & 0.35 & - & {\color{Red} 0.2213 } & {\color{Red} 0.3954 } \\
% SingleLinkage & 0.65 & - & {\color{Red} 0.2177 } & {\color{Red} 0.3889 } \\
% SingleLinkage & 0.60 & - & {\color{Red} 0.2116 } & {\color{Red} 0.3842 } \\
% SingleLinkagePlusCLC & 0.75 & - & {\color{Red} 0.2093 } & {\color{Red} 0.3785 } \\
% SingleLinkage & 0.55 & - & {\color{Red} 0.1987 } & {\color{Red} 0.3700 } \\
% SingleLinkage & 0.50 & - & {\color{Red} 0.1952 } & {\color{Red} 0.3659 } \\
% SingleLinkage & 0.35 & - & {\color{Red} 0.1852 } & {\color{Red} 0.3463 } \\
min T & 0.35  & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\
min F & 0.35  & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Results on cityscapes validation set (with finetuned affinities). \TODO{Reformat in the usual form, delete colors, less digits}}
    \label{tab:linkage-criteria}
\end{table}

% \begin{table*}
%     \centering
%     \begin{subtable}[t!]{0.98\textwidth}\centering
%         \begin{tabular}{c| c| c | c}
%         Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
% GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
% mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
% mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
% MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
% SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
% CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\

%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
%     \label{tab:linkage-criteria}
% \end{table*}

### 2019-03-17 chapters/5_experiments_noise.tex
Add and update graphics

% !TEX root = ../agglo_clust_review.tex
\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
\caption{Plot illustrating results with merge-biased noise...}
\end{figure}

\subsection{Noise experiments}
\begin{itemize}
\item Define Perlin/opensimplex noise
\item Present plots
\item Comment about MC energy
\end{itemize}

\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.27in 0.27in 0.27in 0.27in,clip]{./figs/split_noise.pdf}
\caption{Plot illustrating results with split-biased noise...}
\end{figure}

>>>>

% !TEX root = ../agglo_clust_review.tex
% 
\begin{figure}
\centering
        \begin{subfigure}[t]{0.46 \linewidth}
        \centering
        \includegraphics[width=0.98\textwidth,trim=4.4in 1.2in 0.in 0.05in,clip]{figs/noisy_affs_merge.pdf}
        % \caption{Thresholding of local boundary maps ~(THRESH)} \label{fig:thresh}
    \end{subfigure}%
    \begin{subfigure}[t]{0.46 \linewidth}
        \centering
        \includegraphics[width=0.98\textwidth,trim=4.4in 1.2in 0.in 0.05in,clip]{figs/noisy_affs_split.pdf}
        % \caption{Watershed, seeded at local minima of the smoothed input map~(WS)} \label{fig:ws}
    \end{subfigure}\hspace{0.5cm}%
    \caption{Noisy affinities \TODO{Left: clean affinities. Right: divide image in two triangles and show split and merge simultaneously}}
    % \label{fig:isbi-examples}
\end{figure}%

\subsection{Noise experiments}
\begin{itemize}
    \item In this section we will quantitatively test the robustness of the unified agglomerative clustering algorithm by adding noise to the edge weights of the graph and see how different choices of update rules compare.
    \item Among the update rules listed in Table \ref{tab:linkage-criteria}, we will focus only on \emph{sum}, \emph{arithmetic mean} and \emph{absolute maximum}, since they achieved the best scores in the results presented in Sec. \ref{sec:exp_first_comparison}. Before to present the results shown in Fig. \ref{fig:noise_merge} and \ref{fig:noise_split}, we will first introduce the type of noise that was added to the edge weights.
\item In the set of analyzed experiments, edge weights are estimated \UPDATE{by using a CNN that predicts pairwise interactions between pixels in the image/volume}. Fig. \ref{fig:noisy_affinities}a illustrates the predictions of the CNN for neighboring pixels in the horizontal direction of Define Perlin/opensimplex noise
\item Present plots
\item Comment about MC energy
\end{itemize}

\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.27in 0.27in 0.27in 0.27in,clip]{./figs/split_noise.pdf}
\caption{Plot illustrating results with split-biased noise...}\label{fig:noise_split}
\end{figure}

% \begin{figure}
% \centering
% \includegraphics[width=0.50\textwidth,trim=0.27in 0.27in 0.27in 0.27in,clip]{./figs/noisy_affs.pdf}
% \caption{Illustration of noisy affinities}\label{fig:noisy_affinities}
% \end{figure}

### 2019-03-17 chapters/supplementary.tex
Add and update graphics

>>>>

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{c| c | c| c | c | c | c | c}
Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
% \textbf{mean} & False & \textbf{-102739991} & {\color{Orange} 3797 } & {\color{ForestGreen} \textbf{0.0708} } & {\color{ForestGreen} 0.286 } & {\color{ForestGreen} 0.428 } \\
% % mean & False & -102730208 & {\color{Orange} 2562 } & {\color{ForestGreen} 0.0715 } & {\color{ForestGreen} 0.292 } & {\color{ForestGreen} 0.423 } \\
% MutexWatershed & False & -102313957 & {\color{ForestGreen} 830 } & {\color{ForestGreen} 0.0754 } & {\color{ForestGreen} 0.291 } & {\color{Orange} 0.471 } \\
% sum & False & -101846418 & {\color{Red} 12681 } & {\color{Orange} 0.1623 } & {\color{Orange} 0.427 } & {\color{ForestGreen} 0.427 } \\
% % sum & False & -101732952 & {\color{Red} 12287 } & {\color{Orange} 0.1624 } & {\color{Orange} 0.436 } & {\color{ForestGreen} 0.390 } \\
% sum & True & -101487448 & {\color{Red} 8497 } & {\color{Orange} 0.1626 } & {\color{Orange} 0.428 } & {\color{ForestGreen} 0.414 } \\
% % sum & True & -100745943 & {\color{Red} 13361 } & {\color{Orange} 0.1574 } & {\color{Orange} 0.410 } & {\color{Orange} 0.451 } \\
% mean & True & -100279671 & {\color{Orange} 4713 } & {\color{Orange} 0.1353 } & {\color{ForestGreen} 0.265 } & {\color{Red} 0.717 } \\
% % mean & True & -99416111 & {\color{Orange} 3445 } & {\color{Orange} 0.1761 } & {\color{ForestGreen} 0.260 } & {\color{Red} 0.822 } \\
% max & True & -98143342 & {\color{Red} 7153 } & {\color{ForestGreen} 0.0792 } & {\color{ForestGreen} 0.292 } & {\color{Orange} 0.496 } \\
% max & False & -48601637 & {\color{ForestGreen} 102 } & {\color{Red} 0.9389 } & {\color{Red} 5.738 } & {\color{ForestGreen} 0.035 } \\
% min & False & 210377447 & {\color{ForestGreen} 493 } & {\color{Red} 0.9263 } & {\color{ForestGreen} 0.233 } & {\color{Red} 4.745 } \\
% min & True & 211183545 & {\color{ForestGreen} 692 } & {\color{Red} 0.9221 } & {\color{ForestGreen} 0.232 } & {\color{Red} 4.714 } \\
mean & False & True & -93152163 & {\color{Orange} 3666 } & {\color{Orange} 0.1204 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.641 } \\
sum & False & True & -93142805 & {\color{Red} 16154 } & {\color{ForestGreen} 0.0893 } & {\color{Orange} 0.301 } & {\color{Orange} 0.514 } \\
mean & False &  & -93072127 & {\color{Orange} 3168 } & {\color{Orange} 0.1284 } & {\color{ForestGreen} 0.234 } & {\color{Red} 0.642 } \\
sum & True & True & -92936797 & {\color{Red} 21605 } & {\color{ForestGreen} 0.0910 } & {\color{ForestGreen} 0.293 } & {\color{Orange} 0.532 } \\
MutexWatershed & False &  & -92704851 & {\color{ForestGreen} 632 } & {\color{Orange} 0.1347 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.751 } \\
sum & True & False & -91444880 & {\color{Red} 26842 } & {\color{Red} 0.2085 } & {\color{Red} 0.572 } & {\color{Orange} 0.489 } \\
mean & True & True & -90660193 & {\color{Orange} 4114 } & {\color{Orange} 0.1655 } & {\color{ForestGreen} 0.213 } & {\color{Red} 1.011 } \\
mean & True &  & -88260595 & {\color{Orange} 4393 } & {\color{Red} 0.2017 } & {\color{ForestGreen} 0.208 } & {\color{Red} 1.155 } \\
max & True &  & -81432464 & {\color{Red} 7759 } & {\color{Orange} 0.1653 } & {\color{ForestGreen} 0.236 } & {\color{Red} 0.792 } \\
max & False &  & -37045939 & {\color{ForestGreen} 134 } & {\color{Red} 0.9150 } & {\color{Red} 5.691 } & {\color{ForestGreen} 0.013 } \\
min & False &  & 213670839 & {\color{ForestGreen} 600 } & {\color{Red} 0.9330 } & {\color{ForestGreen} 0.207 } & {\color{Red} 4.880 } \\
min & True &  & 214747429 & {\color{ForestGreen} 852 } & {\color{Red} 0.9314 } & {\color{ForestGreen} 0.202 } & {\color{Red} 4.887 } \\

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Comparison of update rules on crop of cremi sample C (sorted by multicut energy) \TODO{Reduce insane amount of numbers. Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime} }
    \label{tab:linkage-criteria}
\end{table*}
